Named Entity Recognition as Structured Prediction

### 2012-11-10 doc/report/paper.tex
Eval+layout.

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the CoNLL Shared Task 2002 \cite{tksintro} and 
the CoNLL Shared Task 2003 \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
Our approach is based on \cite{strlearn}, of the group that won the challenge for Spanish and Dutch in 2002.

@@

\section{Experiments and Evaluation}
In the following section, we present our experiments and the evaluation of our system.
\subsection*{Experiments}

\subsection*{Evaluation}
For the evaluation of the system we used \emph{Precision} and \emph{Recall} as shown in \ref{Precision} and \ref{Recall} respectively.
Precision is the percentage of Named Entities found by the system that are correct. Recall represents the the percentage of 
named entites present in the corpus that were found by the system. 
A named entity is only deemed correct if it is an exact match for the corresponding data file.
The general formula for the \emph{F-Score} is shown in \ref{Fscore}. Since we rate both \emph{Precision} and \emph{Recall} evenly, we 
use the harmonic mean as shown in \ref{F1}.

\ex. \emph{Precision} = $ \frac{gold\; tag \bigcap predicted}{predicted}$ \label{Precision}\\

\ex. \emph{Recall} = $ \frac{gold \;tag \bigcap predicted}{gold\; tag}$ \label{Recall}\\

\ex. $F_{\beta}$ = $ (1+\beta^2)*\frac{precision *recall}{\beta^2* precision + recall}$ \label{Fscore}\\

\ex. $F_1$ = $ 2*\frac{precision *recall}{precision + recall}$ \label{F1}\\

@@

\section{Discussion of Results}

\section{Future Work \& Conclusion}

>>>>

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the CoNLL Shared Task 2002 \cite{tksintro} and 
the CoNLL Shared Task 2003 \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as BIO-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
%Our approach is based on \cite{strlearn}, of the group that won the challenge for Spanish and Dutch in 2002.

@@

\section{Experiments and Evaluation}

\subsection{Experiments}

\subsubsection{Influence of feature sets}

In the following, we show the influence of each of the three sets of features on the resulting accuracy.

%INSERT MATLAB PIC HERE

\subsubsection{Extending monolingual gazetteers}

% RESULTS FOR DUTCH

\subsection{Evaluation}

@@

For the evaluation of the system, we used the standard measure of \emph{precision} and \emph{recall} as shown below.

\begin{align*}
     precision =  \frac{  |\,gold\,\cap\,predicted\,| }{ |\,predicted\,| } \\
     recall = \frac{ |\,gold\,\cap\,predicted\,| }{ |\,gold\,| }
\end{align*}

Precision is the percentage of Named Entities found by the system that are correct. Recall is the percentage of Named Entities present in the corpus that were found by the system. A Named Entity is only deemed correct if it is an exact match for the corresponding data file. The general formula for the \emph{F-Score} is shown below. Since we consider \emph{precision} and \emph{recall} as equally important, we use the $F_{1}$ score, which is the harmonic mean of precision and recall.

\begin{align*}
  F_{\beta} &=  (1+\beta^2)*\frac{precision *recall}{\beta^2* precision + recall}\\
  F_1       &= 2*\frac{precision *recall}{precision + recall}
\end{align*}

\section{Discussion}

\section{Future Work and Conclusion}
